%-------------------------
% Resume in LaTeX
% Author : Vipun Sanjana Jayathunga
% Purpose: Final resume for GitHub with detailed comments for clarity
%------------------------

\documentclass[letterpaper,11pt]{article} % Standard letterpaper and font size

%-------------------------
% Package imports
%-------------------------
\usepackage{latexsym} % For additional symbols
\usepackage[empty]{fullpage} % Minimal margins
\usepackage{titlesec} % For custom section formatting
\usepackage{marvosym} % For symbols like email/phone icons
\usepackage[usenames,dvipsnames]{color} % Named colors for text
\usepackage{verbatim} % For multi-line comments
\usepackage{enumitem} % Custom lists
\usepackage[hidelinks]{hyperref} % Clickable links without colored boxes
\usepackage{fancyhdr} % For header/footer customization
\usepackage[english]{babel} % English language support
\usepackage{tabularx} % Flexible-width tables
\usepackage{graphicx} % For including images
\usepackage{tikz} % Vector graphics if needed
\input{glyphtounicode} % Ensure correct PDF text encoding for ATS

%-------------------------
% Font settings
%-------------------------
\usepackage{helvet} % Set font to Arial/Helvetica
\renewcommand{\familydefault}{\sfdefault} % Apply sans-serif globally

%-------------------------
% Page layout and margins
%-------------------------
\pagestyle{fancy} 
\fancyhf{} % Clear header/footer
\fancyfoot{} 
\renewcommand{\headrulewidth}{0pt} 
\renewcommand{\footrulewidth}{0pt} 
\addtolength{\oddsidemargin}{-0.5in} 
\addtolength{\evensidemargin}{-0.5in} 
\addtolength{\textwidth}{1in} 
\addtolength{\topmargin}{-.5in} 
\addtolength{\textheight}{1.0in} 

\urlstyle{same} % Keep URL font consistent
\raggedbottom % Avoid vertical stretching
\raggedright % Left-align text
\setlength{\tabcolsep}{0in} % Table column padding

%-------------------------
% Section formatting
%-------------------------
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure PDF is ATS-friendly
\pdfgentounicode=1

%-------------------------
% Custom commands for resume formatting
%-------------------------
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{ % Standard experience/education heading
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\ % Name/Organization and date
    \textit{\small#3} & \textit{\small #4} \\ % Position and optional info
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeCustomSubheading}[2]{ % For simpler headings without dates
  \vspace{2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
  \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubSubheading}[2]{ % For sub-sub entries
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small#2} \\
  \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeProjectHeading}[2]{ % For projects section
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$} % Sub-item bullet style

% List start/end commands for better formatting control
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------
% DOCUMENT START
%-------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Vipun Sanjana Jayathunga} \\ \vspace{2pt}
    % Contact info with clickable links
    \small \href{tel:+94778780559}{+94 77 878 0559} $|$ 
    \href{mailto:vipunsanjana34@gmail.com}{vipunsanjana34@gmail.com} $|$ 
    \href{https://linkedin.com/in/vipunsanjana}{LinkedIn} $|$ 
    \href{https://github.com/vipunsanjana}{GitHub} \\ \vspace{2pt}
    \href{https://www.vipunsanjana.dev}{www.vipunsanjana.dev}
\end{center}

%-----------ABOUT-----------
\section{Personal Profile}
\resumeSubHeadingListStart
    \resumeItem{
    Final-year Software Engineering student at the University of Kelaniya with hands-on experience in backend, frontend, and IoT development. Contributed to AutoSecOps research on AI-driven DevSecOps and interned at WSO2’s Cloud Security Operations Center. Skilled in DevOps, cybersecurity, and Generative AI.}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
    % WSO2 Intern experience
    \resumeSubheading
      {WSO2 - Cloud Security Operations Center (R\&D Software Engineer Intern)}{Oct 2024 -- Apr 2025}{}{}
      \resumeItemListStart
        \resumeItem{R\&D on phishing detection and automation using Python, Ballerina, MongoDB, Docker, Firebase, MySQL, React TypeScript, and Cloud-native services.}
        \resumeItem{Designed automation workflows with Azure Log Analytics, RSA/symmetric encryption, Azure Logic Apps, ServiceNow integrations, and Google Sheets automation.}
        \resumeItem{Deployed microservices on Choreo with scheduled tasks and event-driven triggers, ensuring tested applications and documentation.}
        \resumeItem{Collaborated on internal R\&D initiatives, gaining enterprise security and backend orchestration experience.}
      \resumeItemListEnd

    % Crytec Labs experience
    \resumeSubheading
      {Crytec Labs – Software Developer (Backend \& Mobile)}{Apr 2024 -- Aug 2024}{}{}
      \resumeItemListStart
        \resumeItem{Developed backend modules and APIs using NestJS and supported mobile app development with Flutter.}
        \resumeItem{Contributed to system architecture design, deployment pipelines, and client-facing solutions.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeCustomSubheading
      {University of Kelaniya, Sri Lanka}{July 2022 -- Present}
      \resumeItemListStart
        \resumeItem{B.Sc. (Hons) in Software Engineering, Final Year Undergraduate (GPA: 3.31)}
        \resumeItem{Key Coursework: Problem Solving, Databases, OOP, Data Structures and Algorithms, Full-Stack Web Development, Mobile App Development, Data Science, DevOps, IoT}
      \resumeItemListEnd

    \resumeCustomSubheading
      {Sri Palee College, Horana}{2017 -- 2020}
      \resumeItemListStart
        \resumeItem{G.C.E. Advanced Level – Physical Science (Combined Math – A, Physics – B, Chemistry – B, Z-score: 1.6)}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
    % Example project entry
    \resumeProjectHeading
      {\textbf{\underline{\href{https://github.com/vipunsanjana/Spring-Microservices-Complete-Blueprint}{Spring Microservices Blueprint}}}}{2024}
      \resumeItemListStart
        \resumeItem{Enterprise-grade microservices with service discovery, API Gateway, secure inter-service communication, modular backend. Tech: Spring Boot, Spring Cloud, Eureka, Kafka, Keycloak, Docker, Grafana, Prometheus.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\resumeItemListStart
  \resumeItem{Languages: Python, JavaScript/TypeScript, Java, SQL, Go, Ballerina, KQL, Dart, C, C++, PHP}
  \resumeItem{Frameworks: NestJS, FastAPI, Flask, Flutter, Node.js, Angular, Spring Boot, React, React Native, Express, Next.js, Nuxt.js}
  \resumeItem{Databases: MySQL, MongoDB, Firebase Firestore, MariaDB, Pinecone}
  \resumeItem{Cloud & Infrastructure: AWS, Azure, GCP, Kubernetes, Docker, Terraform, Ansible, Choreo, Nginx}
  \resumeItem{DevOps & Monitoring: Git, GitHub Actions, Argo CD, Jenkins, Grafana, Prometheus}
  \resumeItem{AI/ML: Generative AI, LLMs, RAG, MLOps, scikit-learn, PyTorch, TensorFlow}
  \resumeItem{Tools: Postman, Jira, LaTeX, VS Code, IntelliJ IDEA, Android Studio, Arduino IDE}
  \resumeItem{Platforms: Windows, Linux, Arduino, ESP8266, Raspberry Pi}
  \resumeItem{Soft Skills: Problem Solving, Critical Thinking, Teamwork, Communication, Continuous Learning}
\resumeItemListEnd

%-------------------------
% END OF DOCUMENT
%-------------------------
\end{document}
